Corrections

### 2020-10-01 paper.tex
Now old paper compiles
backup

We start by calculating the first variation. Some calculations are
delegated to Lemma \ref{lemma:aux calc} in the appendix. Also, we
use the following lemma whose proof is also delegated to the appendix:
\begin{lemma}[Generalized from \cite{Lax97}]\label{lemma:lax}
  Let $Y(t)$ be a differentiable operator-valued function. Assume 
  $I+Y(t)$ is invertible, $Y(t)$ self-adjoint and trace-class. Then
  \begin{equation*}
    \frac{\der \log \det (I+Y(t))}{\der t} = \tr (I+Y(t))^{-1} \dot{Y}(t).
  \end{equation*}
\end{lemma}

First variation of $\tar (\obs)$ in the direction $V$ is:
\begin{align*}%%\label{eq:tar var}
  \begin{split}
    \delta \tar(\obs) V 
    :&= \frac{\der}{\der\tau} \Big |_{\tau=0} \tar(\obs + \tau V)\  \text{ (by definition of variation)}\\
    % 
    % 
    % 
    &= \frac12 \frac{\der}{\der \tau} \Big |_{\tau=0} \log \det 
    (I + \prcov^{1/2} \fwd^* T(\obs+\tau V)\fwd \prcov^{1/2} ) \text{ (by definition \eqref{eq:objective})}\\
    % 
    % 
    % 
    &= \frac12 \tr ( I + \prcov^{1/2} \fwd^* \obs^* \Sigma^{-1}
    \obs\fwd \prcov^{1/2} )^{-1}
    \frac{\der}{\der \tau} \Big |_{\tau=0}
    \prcov^{1/2} \fwd^* T(\obs+\tau V) \fwd \prcov^{1/2}\ \text{ (by \ref{lemma:lax})}\\
    % 
    % 
    % 
    &= \frac12 \tr \postcov \fwd^* (
      V^* \Sigma^{-1} \obs 
      - \obs^*\Sigma^{-1} V\modcov \obs^* \Sigma^{-1}\obs \text{ (by \ref{lemma:aux calc})}\\
      &\ \ \ - \obs^* \Sigma^{-1} \obs \modcov V^* \Sigma^{-1}\obs
      + \obs^* \Sigma^{-1} V ) \fwd \\
%%   \end{split}
%% \end{align} 
%% Taking adjoints and cyclic permutations we see that
%% \begin{align*}
%%   \tr \postcov \fwd^* V^* \Sigma^{-1} \obs \fwd 
%%   &= \tr \postcov \fwd^* \obs^* \Sigma^{-1} V \fwd,
%% \end{align*}
%% and
%% \begin{align*}
%%   \tr \postcov \fwd^* \obs^*\Sigma^{-1} V\modcov \obs^* \Sigma^{-1}\obs \fwd
%%   &= \tr \postcov \fwd^*  \obs^* \Sigma^{-1} \obs \modcov V^* \Sigma^{-1}\obs \fwd.
%% \end{align*}
%% We use these in the first equality of the following derivation,
%% which continues the one in \eqref{eq:precursor}.
%% %
%% \begin{align} \label{eq:tar var}
%%   \begin{split}
      %% \delta \tar(\obs) V 
    &= \tr \postcov \fwd^* ( \obs^* \Sigma^{-1} V 
    - \obs^*\Sigma^{-1} V\modcov \obs^* \Sigma^{-1}\obs ) \fwd \\
    %
    %
    % 
    &= \tr \postcov \fwd^* \obs^* \Sigma^{-1} V 
    ( I - \modcov \obs^* \Sigma^{-1}\obs ) \fwd \\
    % 
    %
    %
    &= \tr V ( I - \modcov \obs^* \Sigma^{-1}\obs )
    \fwd \postcov \fwd^* \obs^* \Sigma^{-1}.
  \end{split}
\end{align*} 
Denote
\begin{align}\label{eq:tar grad}
  \nabla \tar(\obs) &:= (I - \modcov \obs^* \Sigma^{-1} \obs) \fwd
  \postcov \fwd^* \obs^*\Sigma^{-1},
\end{align}
the gradient of $\tar (\obs )$ and we now justify this definition.
Since the trace of $A := V \nabla \tar(\obs) \in \R^{m \times m}$ is
just $\tr A = \sum_{j=1}^m e_j^t A e_j$ (with $e_j$ the $j$th standard
basis vector), we see that
\begin{align*}
  \delta \tar(\obs)V = \tr V \nabla \tar(\obs) = \sum_{j=1}^m
  V_j(\nabla \tar(\obs)_j),
\end{align*}
with $V_j \in \ban^*$ and $\nabla \tar(\obs)_j \in \ban^{**}\subseteq
\ban, j=1,\dots,m$. Thus, $\nabla \tar( \obs ) \in (\ban^{**})^m
\subseteq \ban^m$ is indeed the correct gradient and the notation
\eqref{eq:tar grad} is justified. Note that by the comment following
\eqref{eq:obs*}, we view $V$ (defined on the same space as $\obs$) as
a column vector. Then the gradient $\nabla \tar(\obs)$ should be
viewed as a row vector, as the product $V \nabla \tar$ is in $\R^{m
  \times m}$. This will prove important in section
\ref{subsec:necessary}.

@@

The following lemma is generalized from \cite[Chapter 9,
  Theorem 4, pp. 127]{Lax97}
\begin{lemma}\label{lemma:lax}
  Let $Y(t)$ be a differentiable operator-valued function. Assume 
  $I+Y(t)$ is invertible, $Y(t)$ self-adjoint and trace-class. Then
  \begin{equation*}
    \frac{\der \log \det (I+Y(t))}{\der t} = \tr (I+Y(t))^{-1} \dot{Y}(t).
  \end{equation*}
\end{lemma}
\begin{proof}
  Consider a differentiable operator-valued function $X(t)$ such that
  $X(0) = 0$ and $X(t)$ is positive, self-adjoint and trace-class for
  every $t\in \R$. We denote the eigenvalues of this operator by
  $\lambda_k(X(t))$ and sometimes drop the dependence on $X(t)$, so
  $\lambda_k = \lambda_k(X(t))$.  Then $\det (I+X(t)) =
  \prod_{k=1}^{\infty} (1+\lambda_k) < \infty$ where the bound holds
  by the arguments given in \cite{AlexanderianGloorGhattas14}. The
  full derivative is
  \begin{align*}
    \frac{\der \det (I+X(t))}{\der t} 
    % 
    % 
    % 
    &= \sum_{k=1}^{\infty} 
    \frac{\partial \det (I+X(s))}{\partial (1+\lambda_k)}\Big |_{s=t}
    \frac{\der (1+\lambda_k)}{\der t} \\
    % 
    %
    %
    &= \sum_{k=1}^{\infty} \frac{\partial \prod_{l=1}^{\infty}
      (1+\lambda_l(s))}{\partial (1+\lambda_k)}\Big |_{s=t}
    \frac{\der (1+\lambda_k)}{\der t} \\
    %
    %
    %
    &= \sum_{k=1}^{\infty} \frac{\prod_{l=1}^{\infty}
      (1+\lambda_l(s))}{(1+\lambda_k)}\Big |_{s=t}
    \dot{\lambda_k}(X(t)) \\
    % 
    % 
    % 
    &= \sum_{k=1}^{\infty} \frac{\det (I+X(t))}{1 +\lambda_k} \dot{\lambda_k}(X(t)).
  \end{align*}
  The assumption $X(0) = 0$ means $\lambda_k(X(0)) = 0,\ \forall k \geq 1$. Thus:
  \begin{align*}
    \frac{\der (I+\det X(t))}{\der t}\Big |_{t=0} 
    = \sum_{k=1}^{\infty} \dot{\lambda_k}(X(0)) 
    = \frac{\der }{\der t}\tr X(0)
    = \tr \dot{X}(0),
  \end{align*}
  where the second equality follows by monotone convergence. 
  Let $Y(t)$ a trace-class self-adjoint operator such that 
  $I+Y(t)$ is invertible.
  Define $X(t)$ via $I+X(t) = (I+Y(0))^{-1/2} (I+Y(t)) (I+Y(0))^{-1/2}$. 
  We show $X(t)$ satisfies the conditions above. It is trace-class:
  \begin{align*}
    \tr X(t) = \tr \big ( (I+Y(0))^{-1} (I+Y(t)) - I \big )
    \leq \tr \big( I+Y(t) - I \big ) < \infty,
  \end{align*}
  since $Y(t)$ is trace-class. It is also clear that
  $X(0) = 0$ and $X(t)$ is self-adjoint.
  $I+Y(t) = (I+Y(0))^{1/2}(I+X(t))(I+Y(0))^{1/2}$, so
  \begin{align*}
    \frac{\der \det (I+Y(t))}{\der t}|_{t=0} 
    &= \det (I+Y(0))\frac{\der \det (I+X(t))}{\der t}\Big |_{t=0} \\
    % 
    % 
    % 
    &= \det (I+Y(0)) \tr \dot{X}(0) \\
    % 
    % 
    % 
    &= \det (I+Y(0)) \tr (I+Y(0))^{-1} \dot{Y}(0).
  \end{align*}
  Consequently, by the one-variable chain rule:
  \begin{align*}
    \frac{\der \log \det (I+Y(t))}{\der t}\Big |_{t=0} &=
    % 
    % 
    % 
    \frac{1}{\det (I+Y(0))}\frac{\der \det (I+Y(t))}{\der t}\Big |_{t=0} \\ 
    % 
    % 
    % 
    &= \tr (I+Y(t))^{-1} \dot{Y}(t) \big |_{t=0}.
  \end{align*}
  Since there is nothing special about $t=0$, the relation holds for all $t$.
\end{proof}

>>>>

We start by calculating the first variation. Some calculations are
delegated to Lemma \ref{lemma:aux calc} in the appendix. Also, we
use the following lemma whose proof is also delegated to the appendix:
\begin{lemma}[Generalized from \cite{Lax97}]\label{lemma:lax}
  Let $Y(t)$ be a differentiable operator-valued function. Assume 
  $I+Y(t)$ is invertible, $Y(t)$ self-adjoint and trace-class. Then
  \begin{equation*}
    \frac{\der \log \det (I+Y(t))}{\der t} = \tr{(I+Y(t))^{-1} \dot{Y}(t)}.
  \end{equation*}
\end{lemma}

First variation of $\tar (\obs)$ in the direction $V$ is:
\begin{align*}%%\label{eq:tar var}
  \begin{split}
    \delta \tar(\obs) V 
    :&= \frac{\der}{\der\tau} \Big |_{\tau=0} \tar(\obs + \tau V)\  \text{ (by definition of variation)}\\
    % 
    % 
    % 
    &= \frac12 \frac{\der}{\der \tau} \Big |_{\tau=0} \log \det 
    (I + \prcov^{1/2} \fwd^* T(\obs+\tau V)\fwd \prcov^{1/2} ) \text{ (by definition \eqref{eq:objective})}\\
    % 
    % 
    % 
    &= \frac12 \tr ( I + \prcov^{1/2} \fwd^* \obs^* \Sigma^{-1}
    \obs\fwd \prcov^{1/2} )^{-1}
    \frac{\der}{\der \tau} \Big |_{\tau=0}
    \prcov^{1/2} \fwd^* T(\obs+\tau V) \fwd \prcov^{1/2}\ \text{ (by \ref{lemma:lax})}\\
    % 
    % 
    % 
    &= \frac12 \tr \postcov \fwd^* (
      V^* \Sigma^{-1} \obs 
      - \obs^*\Sigma^{-1} V\modcov \obs^* \Sigma^{-1}\obs \text{ (by \ref{lemma:aux calc})}\\
      &\ \ \ - \obs^* \Sigma^{-1} \obs \modcov V^* \Sigma^{-1}\obs
      + \obs^* \Sigma^{-1} V ) \fwd \\
%%   \end{split}
%% \end{align} 
%% Taking adjoints and cyclic permutations we see that
%% \begin{align*}
%%   \tr \postcov \fwd^* V^* \Sigma^{-1} \obs \fwd 
%%   &= \tr \postcov \fwd^* \obs^* \Sigma^{-1} V \fwd,
%% \end{align*}
%% and
%% \begin{align*}
%%   \tr \postcov \fwd^* \obs^*\Sigma^{-1} V\modcov \obs^* \Sigma^{-1}\obs \fwd
%%   &= \tr \postcov \fwd^*  \obs^* \Sigma^{-1} \obs \modcov V^* \Sigma^{-1}\obs \fwd.
%% \end{align*}
%% We use these in the first equality of the following derivation,
%% which continues the one in \eqref{eq:precursor}.
%% %
%% \begin{align} \label{eq:tar var}
%%   \begin{split}
      %% \delta \tar(\obs) V 
    &= \tr \postcov \fwd^* ( \obs^* \Sigma^{-1} V 
    - \obs^*\Sigma^{-1} V\modcov \obs^* \Sigma^{-1}\obs ) \fwd \\
    %
    %
    % 
    &= \tr \postcov \fwd^* \obs^* \Sigma^{-1} V 
    ( I - \modcov \obs^* \Sigma^{-1}\obs ) \fwd \\
    % 
    %
    %
    &= \tr V ( I - \modcov \obs^* \Sigma^{-1}\obs )
    \fwd \postcov \fwd^* \obs^* \Sigma^{-1}.
  \end{split}
\end{align*} 
Denote
\begin{align}\label{eq:tar grad}
  \nabla \tar(\obs) &:= (I - \modcov \obs^* \Sigma^{-1} \obs) \fwd
  \postcov \fwd^* \obs^*\Sigma^{-1},
\end{align}
the gradient of $\tar (\obs )$ and we now justify this definition.
Since the trace of $A := V \nabla \tar(\obs) \in \R^{m \times m}$ is
just $\ttr A = \sum_{j=1}^m e_j^t A e_j$ (with $e_j$ the $j$th standard
basis vector), we see that
\begin{align*}
  \delta \tar(\obs)V = \tr V \nabla \tar(\obs) = \sum_{j=1}^m
  V_j(\nabla \tar(\obs)_j),
\end{align*}
with $V_j \in \ban^*$ and $\nabla \tar(\obs)_j \in \ban^{**}\subseteq
\ban, j=1,\dots,m$. Thus, $\nabla \tar( \obs ) \in (\ban^{**})^m
\subseteq \ban^m$ is indeed the correct gradient and the notation
\eqref{eq:tar grad} is justified. Note that by the comment following
\eqref{eq:obs*}, we view $V$ (defined on the same space as $\obs$) as
a column vector. Then the gradient $\nabla \tar(\obs)$ should be
viewed as a row vector, as the product $V \nabla \tar$ is in $\R^{m
  \times m}$. This will prove important in section
\ref{subsec:necessary}.

@@

The following lemma is generalized from \cite[Chapter 9,
  Theorem 4, pp. 127]{Lax97}
\begin{lemma}\label{lemma:lax}
  Let $Y(t)$ be a differentiable operator-valued function. Assume 
  $I+Y(t)$ is invertible, $Y(t)$ self-adjoint and trace-class. Then
  \begin{equation*}
    \frac{\der \log \det (I+Y(t))}{\der t} = \tr{ (I+Y(t))^{-1} \dot{Y}(t)}.
  \end{equation*}
\end{lemma}
\begin{proof}
  Consider a differentiable operator-valued function $X(t)$ such that
  $X(0) = 0$ and $X(t)$ is positive, self-adjoint and trace-class for
  every $t\in \R$. We denote the eigenvalues of this operator by
  $\lambda_k(X(t))$ and sometimes drop the dependence on $X(t)$, so
  $\lambda_k = \lambda_k(X(t))$.  Then $\det (I+X(t)) =
  \prod_{k=1}^{\infty} (1+\lambda_k) < \infty$ where the bound holds
  by the arguments given in \cite{AlexanderianGloorGhattas14}. The
  full derivative is
  \begin{align*}
    \frac{\der \det (I+X(t))}{\der t} 
    % 
    % 
    % 
    &= \sum_{k=1}^{\infty} 
    \frac{\partial \det (I+X(s))}{\partial (1+\lambda_k)}\Big |_{s=t}
    \frac{\der (1+\lambda_k)}{\der t} \\
    % 
    %
    %
    &= \sum_{k=1}^{\infty} \frac{\partial \prod_{l=1}^{\infty}
      (1+\lambda_l(s))}{\partial (1+\lambda_k)}\Big |_{s=t}
    \frac{\der (1+\lambda_k)}{\der t} \\
    %
    %
    %
    &= \sum_{k=1}^{\infty} \frac{\prod_{l=1}^{\infty}
      (1+\lambda_l(s))}{(1+\lambda_k)}\Big |_{s=t}
    \dot{\lambda_k}(X(t)) \\
    % 
    % 
    % 
    &= \sum_{k=1}^{\infty} \frac{\det (I+X(t))}{1 +\lambda_k} \dot{\lambda_k}(X(t)).
  \end{align*}
  The assumption $X(0) = 0$ means $\lambda_k(X(0)) = 0,\ \forall k \geq 1$. Thus:
  \begin{align*}
    \frac{\der (I+\det X(t))}{\der t}\Big |_{t=0}
    = \sum_{k=1}^{\infty} \dot{\lambda_k}(X(0))
    = \frac{\der }{\der t}\tr X(0)
    = \ttr \dot{X}(0),
  \end{align*}
  where the second equality follows by monotone convergence. 
  Let $Y(t)$ a trace-class self-adjoint operator such that 
  $I+Y(t)$ is invertible.
  Define $X(t)$ via $I+X(t) = (I+Y(0))^{-1/2} (I+Y(t)) (I+Y(0))^{-1/2}$. 
  We show $X(t)$ satisfies the conditions above. It is trace-class:
  \begin{align*}
    \ttr X(t) = \tr{(I+Y(0))^{-1} (I+Y(t)) - I}
    \leq \tr{I+Y(t) - I} < \infty,
  \end{align*}
  since $Y(t)$ is trace-class. It is also clear that
  $X(0) = 0$ and $X(t)$ is self-adjoint.
  $I+Y(t) = (I+Y(0))^{1/2}(I+X(t))(I+Y(0))^{1/2}$, so
  \begin{align*}
    \frac{\der \det (I+Y(t))}{\der t}|_{t=0} 
    &= \det (I+Y(0))\frac{\der \det (I+X(t))}{\der t}\Big |_{t=0} \\
    % 
    % 
    % 
    &= \det (I+Y(0)) \ttr \dot{X}(0) \\
    % 
    % 
    % 
    &= \det (I+Y(0)) \tr (I+Y(0))^{-1} \dot{Y}(0).
  \end{align*}
  Consequently, by the one-variable chain rule:
  \begin{align*}
    \frac{\der \log \det (I+Y(t))}{\der t}\Big |_{t=0} &=
    % 
    % 
    % 
    \frac{1}{\det (I+Y(0))}\frac{\der \det (I+Y(t))}{\der t}\Big |_{t=0} \\ 
    % 
    % 
    % 
    &= \tr (I+Y(t))^{-1} \dot{Y}(t) \big |_{t=0}.
  \end{align*}
  Since there is nothing special about $t=0$, the relation holds for all $t$.
\end{proof}

### 2020-10-01 reply.tex
backup

\begin{itemize}
\item Page 1, Line 39: "In a frequentist settings" should be changed
  to "in a frequentist setting" or "in frequentist
  settings".
  \ydnote{\item Changed in text}

\item Page 2, Line 36: Add a comma: "In the process, we generalize..."
  \ydnote{changed in text}

\item Page 3, Line 37: "with homogeneous Dirichlet boundary condition"
  should be changed to "with a homogeneous Dirichlet boundary
  condiiton". \ydnote{\item Changed}

\item Page 4, Line 14: In equation (2.1), $\Sigma$ has not been
  defined. Please formally define this before giving the equation.
  \ydnote{\item Moved the equation after $\Sigma$ is defined}

\item Page 4, Line 21: The prior distribution $\mathcal{N}(0,
  \Gamma_{pr})$ assumes the prior mean is 0. This is worthy of some
  comment. Why must the prior mean be 0?
  \ydnote{\item It does not have to be, we can subtract the mean. An explanation was added}

\item Page 5, Line 15: Add a comma: "Considering the sum of the error
  terms, it is easy..."
  \ydnote{\item Changed in text}

\item Page 6, Line 7: Please describe what $\psi$ is in the
  theorem. It is defined mathematically but not described. Only much
  later is it stated that this is the objective
  function.
  \ydnote{\item Added comment before statment of theorem where
    $\tar$ first appears}

\item Page 6, Line 19-20: "In section 3.2 we relax the constraints on
  $\mathcal{O}$ so that the optimization problem in (3.1) and find
  gradients for the new constraints." This sentence is unclear and
  should be reworded.
  \ydnote{\item Added short explanation}

\item Page 7, Line 24, 27, 31: The proposition is labeled as
  Proposition 1, but it is refered to as Proposition 2, and relabeled
  Proposition 2 in the appendix.
  \ydnote{\item All such errors were fixed}

\item Page 9, Line 6: Please be more exact when refering to "the big
  parentheses" to avoid any chance of confusion. Give the explicit
  formula here as you do for another term earlier in the sentence.
  \ydnote{\item Explicit expression given}

\item Page 18, Line 6: This proposition was previously labeled
  Proposition 1. \ydnote{\item All such errors were fixed}
\end{itemize}

@@

\begin{enumerate}
\item line 30: the author claims to present an analytically tractable
  model for understanding D-optimal designs. By reading the paper, I
  couldn't figure out how this reflects to any practical scenario. I'm
  not sure how this can be utilized for example in spatial sensor
  placement problems. An algorithmic description would be very useful
  here.

@@

In Equation 4.3, not sure what $\fwd^{-*}$ stands for. Moreover, an
inverse of the forward operator is not well-defined even if
$\mathcal{F}\Gamma_{prior}\mathcal{F}^*$ is invertible! This is very
limiting, and can't be used in practical inverse problems. This should
be clearly discussed for the reader to appreciate the valuable effort
made. \ydnote{Again, great point. $ \fwd^{-*} = (\fwd^*)^{-1}$ but now
  I do not assume $\fwd$ is invertible so this is removed}

@@

I found it difficult to trace the referenced Lemmas, Corollaries,
etc., mainly because bad referencing in the appendix, and the links do
not works properly.  For example Corollary 2 should be Corollary B.x,
etc. \ydnote{All such bad references were fixed}

The trace operator should be followed with some sort of brackets to
make it easier to follow and validated the formulae
\ydnote{curly brackets added everywhere}

>>>>

\begin{itemize}
\item Page 1, Line 39: "In a frequentist settings" should be changed
  to "in a frequentist setting" or "in frequentist
  settings".
  \ydnote{Changed in text}

\item Page 2, Line 36: Add a comma: "In the process, we generalize..."
  \ydnote{Changed in text}

\item Page 3, Line 37: "with homogeneous Dirichlet boundary condition"
  should be changed to "with a homogeneous Dirichlet boundary
  condiiton". \ydnote{Changed}

\item Page 4, Line 14: In equation (2.1), $\Sigma$ has not been
  defined. Please formally define this before giving the equation.
  \ydnote{Moved the equation after $\Sigma$ is defined}

\item Page 4, Line 21: The prior distribution $\mathcal{N}(0,
  \Gamma_{pr})$ assumes the prior mean is 0. This is worthy of some
  comment. Why must the prior mean be 0?
  \ydnote{It does not have to be, we can subtract the mean. An explanation was added}

\item Page 5, Line 15: Add a comma: "Considering the sum of the error
  terms, it is easy..."
  \ydnote{Changed in text}

\item Page 6, Line 7: Please describe what $\psi$ is in the
  theorem. It is defined mathematically but not described. Only much
  later is it stated that this is the objective
  function.
  \ydnote{Added comment before statment of theorem where
    $\tar$ first appears}

\item Page 6, Line 19-20: "In section 3.2 we relax the constraints on
  $\mathcal{O}$ so that the optimization problem in (3.1) and find
  gradients for the new constraints." This sentence is unclear and
  should be reworded.
  \ydnote{Added short explanation}

\item Page 7, Line 24, 27, 31: The proposition is labeled as
  Proposition 1, but it is refered to as Proposition 2, and relabeled
  Proposition 2 in the appendix.
  \ydnote{All such errors were fixed}

\item Page 9, Line 6: Please be more exact when refering to "the big
  parentheses" to avoid any chance of confusion. Give the explicit
  formula here as you do for another term earlier in the sentence.
  \ydnote{Explicit expression given}

\item Page 18, Line 6: This proposition was previously labeled
  Proposition 1. \ydnote{All such errors were fixed}
\end{itemize}

@@

\begin{enumerate}
\item line 30: the author claims to present an analytically tractable
  model for understanding D-optimal designs. By reading the paper, I
  couldn't figure out how this reflects to any practical scenario. I'm
  not sure how this can be utilized for example in spatial sensor
  placement problems. An algorithmic description would be very useful
  here.
  \ydnote{Unfortunately, this work does not have
    immediate applications to (e.g.) spatial sensor placement
    problems. I offer a toy model for understanding sensor
    clusterization. I plan to use some of the conclusions in
    subsequent work but I find it out of scope for the work under
    consideration here.}

@@

In Equation 4.3, not sure what $\fwd^{-*}$ stands for. Moreover, an
inverse of the forward operator is not well-defined even if
$\mathcal{F}\Gamma_{prior}\mathcal{F}^*$ is invertible! This is very
limiting, and can't be used in practical inverse problems. This should
be clearly discussed for the reader to appreciate the valuable effort
made.
\ydnote{Again, great point. $\fwd^{-*} = (\fwd^*)^{-1}$ but now I do
  not assume $\fwd$ is invertible so this is removed}

@@

I found it difficult to trace the referenced Lemmas, Corollaries,
etc., mainly because bad referencing in the appendix, and the links do
not works properly.  For example Corollary 2 should be Corollary B.x,
etc.
\ydnote{All such bad references were fixed.}

The trace operator should be followed with some sort of brackets to
make it easier to follow and validated the formulae
\ydnote{Curly brackets added where needed.}
